
% --- Acknowledgment ---
\begin{CJK*}{UTF8}{bkai}
\begin{center}
\Large
\textbf{誌~~~~~~謝}
\end{center}

\vspace{1cm}
\linespread{2}%
\selectfont
\hspace{0.25cm}
深深感謝所有在完成這篇論文的過程中，給予我指導、鼓勵和支持的人。特別要感謝在機器學習及深度學習領域有豐富經驗的洪哲倫老師，對整個研究提供非常多建議，過程中也不斷鼓勵我嘗試許多最先進的技術，從中真的獲益良多。同時，也要感謝另一位指導教授吳俊穎老師，在碩班期間不斷支持我鑽研自然語言處理領域的研究，也在自己繁忙的研究中，仍抽空提供許多應用的重要建議，擴展研究的應用價值。兩位老師的指導和帶領，都讓我能更深入看見生物醫學資訊領域研究的各樣細節，從而培養提出問題和解決問題的能力。

此外，還要感謝巫坤品老師和林俊淵老師，針對研究提供許多寶貴意見。巫老師深入並嚴謹的建議，使我能用更客觀更正確的方式呈現研究，思考每一個步驟的理由與合理性，林老師的回饋也提點我許多研究中沒有考慮到的方向，幫助我不斷加強論文的深度與廣度。

也要感謝實驗室的學長姊、學弟妹們，兩年當中許多的陪伴和歡笑，有了這群夥伴的協助與合作，為這段學術旅程留下許多回憶。最後也謝謝我的父母和哥哥，在我因研究感到緊繃的時期成為最溫暖的避風港，讓我有勇氣繼續前進，也是支撐我堅持追求卓越的最大動力。一路上受到太多人幫助，也是提醒自己還有很多不足之處，需要保持謙卑、繼續成長，真誠地感謝所有人在整個學術追求過程中給予的支持和幫助，謝謝。

% I am deeply grateful to everyone who has provided guidance, encouragement, and support throughout the process of completing this thesis. I especially want to thank Prof. Che-Lun Hung, who has an extensive machine and deep learning experience. He offered numerous valuable suggestions for the entire research process, constantly encouraging me to explore state-of-the-art technologies, which has greatly helped me. Additionally, I am grateful to another advisor, Prof. Chun-Ying Wu, who supported my research in natural language processing during my graduate studies. Despite his busy schedule, he still found time to provide crucial advice on practical applications, expanding the research's value. The guidance of both professors has allowed me to delve deeper into the various aspects of biomedical informatics research, growing my ability to identify and solve problems.
% Furthermore, I express my gratitude to Prof. Kun-Pin Wu and Prof. Chun-Yuan Lin for their roles as members of my thesis committee. Their in-depth feedback was instrumental in enabling me to present the research more objectively and accurately, while Prof. Lin's feedback also directed me toward considerations I hadn't previously explored, significantly strengthening the depth and breadth of the thesis.
% Finally, I appreciate the assistance and collaboration of my lab partners, who have contributed to many memorable moments during this academic journey. My parents' constant encouragement has been the greatest motivation in my pursuit of excellence. I sincerely thank everyone for their support and help throughout this academic pursuit.

\vspace{2cm}
\begin{flushright}
陳建安　於

國立陽明交通大學生物醫學資訊研究所碩士班

中華民國 \, 113 年 \, 7 \,月
\end{flushright}
\end{CJK*}
